\documentclass[a4paper,9pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{fontawesome}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}

\addtolength{\oddsidemargin}{-0.65in}
\addtolength{\evensidemargin}{-0.65in}
\addtolength{\textwidth}{1.3in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.3in}

\linespread{0.9}
\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
    \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%----------------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeItemWithoutTitle}[1]{
    \item\small{
        #1 \vspace{-2pt}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
            \textbf{#1} & #2 \\
            \textit{#3} & \textit{#4} \\
        \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------------------
% CV Starts

\begin{document}

%-----------------------------------------
% Heading

\begin{center}
    \textbf{{\LARGE Anshul Jain}} \\
    \vspace{3pt}
    \scriptsize{
        \faLinkedin \hspace{2pt} \textcolor{blue}
        {\href{https://www.linkedin.com/in/theanshuljain/}{anshul-jain}} \hspace{5pt}
        \faGithub \hspace{2pt} \textcolor{blue}
        {\href{https://github.com/theanshuljain}{Anshul-Jain}} \hspace{5pt}
        \faEnvelope \hspace{2pt} \textcolor{blue}{\href{mailto:anshuljain6598@gmail.com}{anshuljain6598@gmail.com}} \hspace{5pt}
        \faPhone \hspace{2pt} +1 (206) 600-1808 \hspace{5pt}
        \faMapMarker \hspace{2pt} Boulder, CO, USA
  }
\end{center}

%------------------------------------------
% Objective

\section{Objective}
\begin{justify}
Driven and hardworking professional with a strong foundation in Engineering Mathematics, Physics, and System Design. As a Graduate Aerospace Engineer and passionate educator, I am eager to take on new challenges that allow me to utilize my skills in strategic planning, training and development, relationship building, and project management. Proven ability to lead cross-functional teams, mentor peers, and simplify complex technical concepts into accessible lessons and hands-on demonstrations. Committed to showing up as my authentic self, following my passions, and adding meaningful value to every role I undertake. Seeking teaching opportunities where I can use my background and expertise to inspire curiosity, analytical thinking, and a lifelong love for learning in students.
\end{justify}

%------------------------------------------
% Education

\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{University of Colorado Boulder}{Aug 2023 – Dec 2025}
{Master’s in Aerospace Engineering Sciences}{Boulder, CO}

\resumeSubheading
{R. V. College of Engineering}{Aug 2019 – Apr 2023}
{Bachelor’s in Aerospace Engineering}{Bengaluru, India}

\resumeSubHeadingListEnd

\textbf{Programming and Tools:} MATLAB, Simulink, Python, C, C++, JavaScript, R, VS Code, Git, GitHub, Canvas.

%-------------------------------------------
% Research Experience
\section{Research Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Co-Author, 73rd International Astronautical Congress}{Nov 2021 – Sept 2022}
{Team Antariksh}{Bengaluru, India}
\resumeItemListStart
\resumeItemWithoutTitle{Vageesha S, Darpan B, Trisha A, Anshul Jain, Greeshma A, Rithwik R, “Study of Drag Characteristics of a Parachute for landing on planets and moons with different atmospheric conditions and its optimization using gases with varying properties”.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
% Awards and Recognition
\section{Awards and Recognition}
\resumeSubHeadingListStart

\resumeSubheading
{SAARTHAKA Trust Scholarship}{Jan 2020}
{R. V. College of Engineering}{Bengaluru, India}
\resumeItemListStart
\resumeItemWithoutTitle{Awarded for securing \textbf{Rank 1 in Aerospace Engineering (2019)} among all first-year students.}
\resumeItemListEnd

\resumeSubheading
{E-Summit Business Marathon – 1st Place}{July 2022}
{R. V. College of Engineering}{Bengaluru, India}
\resumeItemListStart
\resumeItemWithoutTitle{Ranked \textbf{1st out of 32 teams} for developing a service-based transport solution addressing damaged road infrastructure in hilly regions during monsoon conditions.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------
% Volunteer Experience
\section{Volunteer Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Emcee – Faculty Development Program (FDP)}{May 2022}
{R. V. College of Engineering}{Bengaluru, India}
\resumeItemListStart
\resumeItemWithoutTitle{Coordinated a 5-day FDP on Machine Learning applications in Aerospace Engineering, facilitating sessions, managing logistics, and ensuring smooth communication between faculty and participants.}
\resumeItemListEnd

\resumeSubheading
{Emcee – RSS Vishwa Sangh Shibir}{Dec 2015}
{Rashtriya Swayamsevak Sangh}{Indore, India}
\resumeItemListStart
\resumeItemWithoutTitle{Served as the Tamil-language Emcee for the international conference, engaging with delegates from 45+ countries after rapidly acquiring conversational proficiency in the language.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------
% Languages
\section{Languages}
\resumeItemListStart
\resumeItemWithoutTitle{English: Professional Proficiency}
\resumeItemWithoutTitle{Hindi: Native Proficiency}
\resumeItemListEnd

%-------------------------------------------
\end{document}